\section{Libraries}

The program uses a number of external libraries to achieve its functionality. This section describes which they are,
how they interact with the program, as well as licensing information. 

\subsection{Java play}
\textbf{Version:} 2.0.4

\textbf{Link:} \url{http://www.playframework.org/}

\textbf{Usage:} 
Java play is primarily a web framework, but it includes a webserver too.
We use it to create a modern, dynamic and interactive website, instead of a conventional java Swing GUI.
Our web server tier is just a modification of appropriate java play classes.

\textbf{License:} Apache 2 License
\subsection{D3.js}
\textbf{Version:} 2

\textbf{Link:} \url{http://d3js.org/} 

\textbf{Usage:} 
D3.js is a javascript visualization library for the browser.
It allows the creation of beautiful, interactive visualizations.
It is used, as one would imagine, in our browser tier.

\textbf{License:} BSD License, Clause 3


\subsection{GeoIP}\label{geo}

\textbf{Version:} 1.2.8

\textbf{Link:} \url{https://www.maxmind.com/download/geoip/api/java/}

\textbf{Usage:} 
We use the Maxmind GeoIP Lite library to map user IPs to locations.
This allows queries based on location, as well as preserving anonymity.
Our parser uses the GeoIP library.

\textbf{License:} LGPL

\subsection{Oracle Data Warehouse \& OLAP software}
\textbf{Version:} 11g Release 2

\textbf{Link:} \href{http://www.oracle.com/de/technologies/datawarehousing/index.html}{Oracle Data Warehousing}

\textbf{Usage:} 
Data will be stored with an Oracle warehouse and Oracle OLAP-Cubes. We will use the software over the KIT.

\textbf{License:} Oracle license
% 
% \subsection{Licensing information}
% Most of the libraries used are open source, as well as free of charge.
% The rest are from Oracle. We can use them in our product, because our university has bought licenses 
% but I don't know what happens when we release it. 
% 
% Java play is released under the Apache 2 License [apache2]
% d3.js is released under the BSD License, BSD 3 Clause [bsd3]
% The geoip library we use is licensed under the LGPL. [lgpl]
% 
% Oracle libraries are released under the oracle license[oracle]


% [d3link] d3js.org
% [geo] http://www.maxmind.com/download/geoip/api/java/
% [oracle] http://www.oracle.com/technetwork/licenses/distribution-license-152002.html.
% [apache2] http://www.apache.org/licenses/LICENSE-2.0.html
% [bsd3]  http://opensource.org/licenses/BSD-3-Clause
% [lgpl] http://opensource.org/licenses/lgpl-license
