\section{Data} % name to be discussed
The program along with its libraries gets compiled to an executable .jar file.
However, it also uses a number of external data.

\subsection{Log files}
Log files are arguably the most important data files our program has to deal with, since it simply
needs them to function properly.

They have to be valid .csv files as well as be consistent with the configuration files specified. 
For more information on configuration files, read on.

\subsection{Configuration files}
This fulfills optional requirements.

The program may work with more database log files than just with these from the SkyServer without 
any modifications to its source code.
However, to achieve this functionality configuration files have to be read. 
A configuration file needs to be written per database.

The configuration file contains, among others, the database schema, the dimensions and 
measures used as well as their types.

Additionally, we will provide a sample configuration file for the skyserver, 
as well as documentation on creating one.


\subsection{Visualization files}
The program dynamically recognizes javascript visualization files during its startup, provided
they are created with our specifications in mind and are either placed in the appropriate directory structure,
or are uploaded through the admin panel.
That said, this allows new chart types, or different visualizations to be created by a user simply by providing
the javascript file. Javascript files have a .js ending.

\subsection{Language files}
Our program keeps language files separate to enable a smooth translation and
maintenance of the graphical user interface.

\subsection{Misc}
Favicons, logos, thumbnails for the chart types are also used.
