

\subsection*{General Information}
%\subsection*{Why this specification is written}
\gls{PSE} is a mandatory course for students of computer science bachelor at the % Glossary: PSE, KIT
Karlsruhe Institute of Technology (\gls{KIT}). Therefor groups of five to six
students are formed to write programs of 'medium size' (about 5000 Lines of Code). 
The task given in this course consists of analyzing and visualizing the server log of a \gls{database}.

This specification is the one of \gls{PSE} Group \#10 in the winter semester 2012/13.


%\subsection*{Content of this specification}
\subsection*{What this specification does}
The purpose of this document is an outline of the functional specifications and requirements
for the WHAT application. It tries to give a complete and exact model of the future system.
In the course of this it wants to give the developers answers to all possible question concerning
what should be implemented.


\subsection*{What this specification does not}
This specification does not give any information on how the system should be implemented. 
Also it doesn't contain any project planning or deadlines.


\subsection*{A 'Living Document'}
Software development is a dynamic process. So with proceeding development the
content of this specification will change continuously. 


\subsection*{Skyserver}
The concept of the system described in this specification should work with any \gls{database}
storing it's query-log. The \gls{SkyServer} will function
as an example and testing reference for this system. 
\gls{SkyServer} is one of the biggest \glspl{database} for astronomical data.
 
\subsection*{About us}
%\subsection*{About the writers}
Because no one of us speaks English as his first language,
we can't guarantee that our documentation doesn't contain simple
or incorrectly used language. Our focus lies more on
having an easy-to-understand and correct documentation
than on perfect English.% by a native speaker.

% \subsection*{Questions and comments}
If you have any questions or comments regarding this document feel free to send us an 
 \href{mailto:pse10-group14-ws12@ira.uni-karlsruhe.de}{E-Mail}.







 
% \newpage
% \section*{Introduction} % obsolet?
% PSE is a mandatory course for students of Bachelor Informatik in the
% Karlsruhe Institute of Technology (KIT).
% In this course we have to form groups of five or six people to write
%  a program of 'medium size' ($\sim$5000 Lines of Code).
% 
% Our task given in this course consists of
% analyzing and visualizing the server log of the
% \href{http://skyserver.sdss.org/public/en/}{SkyServer}.
% This is one of the biggest public databases for astronomical data.
% It contains pictures and informations of astronomical data
% and tries to form a 'map of the universe'.
% 
% This assignment is one of two assignments which will be handled
% in English.
% Because no one of us speaks English as his first language,
% we want to apologize that our documentation may contain simple
% or in some parts incorrectly used language. Our focus lies more on
% having easy-to-understand and correct documentation
% than on perfect English, which looks like written by a native speaker.
% 
% We are going to write a web-frontend in javascript allowing users
% to access the finished application from everywhere
% with recent browsers. The actual application can be spliited into two
% different parts. The first part - which will be referred as 'Parser' and is going to convert the CSV-formatted
% serverlog from Skyserver into a data-warehouse. It will
% be accessible via admin-login to the webpage where we can enter a
% logfile, which will be parsed into our warehouse.
% The second part - which will be referred as 'Analyzer' works on this data-warehouse
% and allows every user of our webpage to create various charts,
% for example scatterplots and histograms.
% Due to the fact that we split our project in two smaller parts,
% many parts of this specification are going to be splitted in two.
% 
% We have to state that no one of us has much experience in working
% with databases and javascript.
% Therefore we can't guarantee the correctness of all information
% stated in this specification. Some of the specifications may be altered when we design or
% implement the actual program.
