\section{Goals}

%=======================================================================
 
With this program the user should be put in the position 
to visualize the prepared data of \glspl{query}, made into his \gls{database}.


To structure the criteria the system has to fulfill, 
it is divided into three parts for this and other sections.
\begin{itemize}
  \item Web page
  \item \gls{parser}
  \item Analyzer
\end{itemize}
See \ref{overview} for an overview of these parts and their relationships.
In the following section their specific goals and criteria are described.
 

% \subsection{Core criteria}
% This criteria have to be fulfilled to guarantee 
% the core functionality of the system.
% 
% \begin{itemize}
%   \item Provide an option to import CSV-formatted log files % glossary
%    and parse specified data out of them
%   \item Load 
% \end{itemize}


%=======================================================================
\subsection{Web page}
\subsubsection{Core criteria}
\begin{itemize}
\item The web page is the graphical user interface (\gls{GUI}) for users and administrators. 

\item Users can choose the \glspl{chart} they want to see 
and also choose and filter the \glspl{dimension} and \glspl{measure} for those. 
It has to support at least \glspl{scatter plot}, \glspl{bar chart} and \glspl{bubble chart}.

\item The web page provides help for how to use the \glspl{diagram} and variables (\glspl{dimension} 
and measures). 
Also the navigation on the page is easy to use and straight forward.

\item An admin-login provides administrative rights, which are needed to use the \gls{parser}.
\end{itemize}

%----------------------------------------------------------------------
\subsubsection{Optional criteria}
\begin{itemize}
\item The language of the web page can be changed (e.g. German).

\item The administrator gets the ability to handle the \gls{data warehouse} and load new \glspl{log file}.

\item A little history of the last requested \glspl{chart} is stored and viewable.

\item You can download a picture of a created charts.
\end{itemize}

%----------------------------------------------------------------------
\subsubsection{Exclusion criteria}
\begin{itemize}
\item The web page does not allow normal users to load new data into the \gls{data warehouse}.

\item The web page does not provide statistical tables. 
\end{itemize}


%=======================================================================
\subsection{Parser}

\subsubsection{Core criteria} % Musskriterien
\begin{itemize}
\item The \gls{parser} is able to perform the \gls{ETL-process} on \gls{.csv} \glspl{log file}
 (from \gls{SkyServer}). 
This means it extracts the data it needs from the files, transforms them 
and loads them into the \gls{data warehouse}. \gls{dimension} and \glspl{measure} are specified in \ref{WHschema}.
  
\item The \gls{parser} will recognize invalid logs and won't add them to the \gls{data warehouse}.
 Every log with a mistake won't be accepted, because an error-message is not 
 as bad as a corrupted \gls{data warehouse}. 
 
\item The \gls{parser} will be fed with \glspl{log file} from the administrator via web page.
\end{itemize} 

% %----------------------------------------------------------------------
% \subsubsection{Optional criteria}
% \begin{itemize}
% \item 
% \end{itemize} 
 
%----------------------------------------------------------------------
\subsubsection{Exclusion criteria}
\begin{itemize}
\item This \gls{parser} is only able to operate on \gls{.csv} \glspl{log file} from \gls{SkyServer}. 
It can neither read logs in another formats nor logs from another source.

\item There is no way to avoid using this \gls{parser} when adding data to the \gls{data warehouse}. 
This prevents corrupting the \gls{data warehouse} and guarantees correct data in it.

\item The \gls{parser} doesn't correct mistakes in the \glspl{log file}.
\end{itemize}



%=======================================================================
\subsection{Analyzer}

\subsubsection{Core criteria}
\begin{itemize}
\item The analyzer is the gate to the \gls{data warehouse}. It extracts the specific data, 
needed for the \glspl{diagram}, passing them to the java-script front-end.
\item The analyzer can take information filtered by user-selected criteria, 
to use only certain data for the \glspl{chart}.
\item The \glspl{chart} that are supported are at least:
\begin{itemize}
\item \glspl{scatter plot}
\item \glspl{bar chart}
\item \glspl{bubble chart}
\end{itemize}

\end{itemize}

%----------------------------------------------------------------------
\subsubsection{Optional criteria}
\begin{itemize}
\item The analyzer will support more chart-types, for example the combination of
a \gls{bar chart} and a \gls{scatter plot}. 
\item The analyzer does a little bit of data mining, and presents some potentially interesting information.
\end{itemize}

%----------------------------------------------------------------------
% \subsubsection{Exclusion criteria}
% \begin{itemize}
% \item 
% \end{itemize}


% Vll sollte man noch was zum warehouse sagen.



