\section{Operating environment}



%You keep using that word. I don't think it means what you think it means
% http://en.wikipedia.org/wiki/Workstation
Whereas the program and the data warehouse run on a server,
the access to it will be via a web browser on the users computer. 
This implies that the webpage will need to be hosted on a webserver.
However, a dedicated server machine is not required, as the clients computer can 
host both the client and the webserver, and then access the webpage locally.



\subsection{Software}
\begin{itemize}
  \item The server hosting the data warehouse needs SQL support. %glossary
  
  \item The server hosting the web server needs a 
  recent version of the Java Runtime Environment / Java VM  % Glossary
\end{itemize}


Following software is required on the users computer:
\begin{itemize}
  \item Latest version of a modern browser
  \begin{itemize}
    \item Though Chrome and Firefox will be officially supported, other browsers might work as well.
  \end{itemize}
  \item JavaScript (enabled)
\end{itemize}



\subsection{Hardware}

The server has to be fast enough to support all clients. This depends on
the expected number of clients. Most computations will be done on the server.

% Is the program really local hosted? %wat
The client needs to be fast enough to visualize the data received from the server, as that's almost all it does.
The required hardware thus depends greatly on the amount of data that needs to be 
visualized. That said, any recent computer, with for example, 
an Intel® Core™2 Duo CPU E8400 @ 3.00GHz × 2 processor, 
4GB(2x2GB) of 667Mhz DDR2 SDRAM, running Ubuntu Linux 12.10 Quantal Quetzal, 
% this was, like, a joke, because it's, like, my computer
as a point of reference, should be able to visualize about 50.000 
data points on a scatterplot with ease.


\subsection{Orgware}

The server needs to be able to connect to the client with a reasonable latency.
Also it has to be set up before the client is able to connect to it.

% Other direction: Program hast to be able to run query against data warehouse?

To fulfill optional requirements, the program must be able to run queries against
the origin database. //FIXME I DON'T KNOW ABOUT THAT

% \subsection{Product interfaces}
% 
% To fulfill optional requirements .csv files have to be imported.