\section{Test Cases}

\subsection{Global test cases}

% Enumeration changed
\renewcommand{\theenumi}{/T\arabic{enumi}0/}
\renewcommand{\labelenumi}{\theenumi}

\subsubsection{General}

Those test-cases are necessary for the webpage to work 
properly and succeed in serving basic requests.

\begin{enumerate}

\item Access web page (local or internet) (\ref{f1})
\begin{enumerate}
  \item[/T12/] via Google Chrome
  \item[/T14/] via Mozilla Firefox
\end{enumerate}
\label{t10}

\item Navigate switfly through the web page. (\ref{f141}) 
\label{t11}

\item Open page for scatter plot-creation and create an example
      with x-Axis date and y-Axis number of lines per request. (\ref{f2}, \ref{f3}, \ref{f7}, \ref{f9})
\label{t12}

\item Open page for histogram-creation and create an example
      with x-Axis year and y-Axis number of requests. (\ref{f2}, \ref{f3}, \ref{f4}, \ref{f6})
\label{t13}

\item Open page for bubble chart-creation and create an example
      with x-Axis year, y-Axis Country and size number of requests. (\ref{f2}, \ref{f3}, \ref{f10}, \ref{f11})
\label{t14}

\item Call the information about chart types. (\ref{f13})
\label{t15}

\item Request information about selectable variables. (\ref{f14})
\label{t16}

\end{enumerate}

\subsubsection{Administrator specific}

Those test cases check the correct admin-login.

\begin{enumerate}[resume]

\item Enter loginname and password for admin-login. (\ref{f15})
\label{t17}

\item Log-in and get administrative rights. (\ref{f15})
\label{t18}

\item Try to log in with wrong loginname. (\ref{f15})
\label{t19}

\item Try to log in with wrong password. (\ref{f15})
\label{t20}

\item Pass example log-file to the parser. (\ref{f16})
\label{t21}


\end{enumerate}

\subsubsection{Parser specific}

The following test cases test the correct work of our parser.
%, which extracts information from a .csv-file and writes 
%it in our data-warehouse.

\begin{enumerate}[resume]

\item Parse example log-file and extract valuable information correctly. (\ref{p1})
	\\ More specifically: 
\label{t22}
  \begin{enumerate}

	\item[/T132/] Extract correct database, time, user information 
	and type (\ref{p2})
\label{t23}

	\item[/T134/] Extract correct number of rows, elapsed time, 
	busy time from the log-file (\ref{f17})
\label{t24}	
	
	\item[/T136/] Extract the type requested (\ref{p4})
\label{t25}

  \end{enumerate}

\item Load extracted information into the data warehouse correctly. (\ref{f18}, \ref{f19})
\label{t26}

\end{enumerate}


\subsubsection{Analyzer specific}

The functions  \ref{f20} and \ref{f21} of the analyzer are 
already tested in the general test-cases \ref{t12} to \ref{t14}.



\subsection{Scenario Testing}

Scenario testing is sequence Workflow from use cases and shod lead iteratively

% Enumeration changed
\renewcommand{\theenumi}{/T\arabic{enumi}0/}
\renewcommand{\labelenumi}{\theenumi}

\subsubsection {Scenario 1: loading logs file} 

\begin{enumerate}
 
\item Start the Application

\item Log in the User with the Admin ID and password

\item Write the Queries

\item Send the Querise to Skyserver

\item Send the logs file to parse

\item Call the opportunity to initialize the data warehouse

\item Call the opportunity to request new log-files for specific time intervals from the
database

\item Call the opportunity to clean the data warehouse %what's mean?

\item Leave the Application

\end{enumerate} 

\subsubsection {Scenario 2: parsing} 

\begin{enumerate}

\item Start the Application

\item Log in the User with the Admin ID and password

\item Call Extract specific data from the log-files

\item Call Extract access database, access time and user information (dimensions)

\item Call Extract number of rows, elapsed time, busy time (measures)

\item Call Extract type of data requested from the where-part

\item Call Transform the data to fit into the data warehouse schema

\item Load the data into the data warehouse

\item Leave the Application 

\end{enumerate} 

\subsubsection {Scenario 3: selecting variables of diagrams} 

\begin{enumerate}

\item Start the Application

\item Select a diagram type

\item Show the diagram

\item Call option for the tow or three variables of the diagram

\item Change one, tow or three variables of the diagram

\item Refresh the Information

\item Show the new diagram with new variables of the diagram

\item Leave the Application

\end{enumerate}

\subsubsection {Scenario 4: options} 

\begin{enumerate}

\item Start the Application

\item Call the option menu

\item Select the Languge of the Application

\item Show the Application with the selected languge

\item Leave the Application

\item Start the Application 

\item Select the diagram 

\item Call file menu

\item Save the diagram as a PDF file

\item Leave the Application

\end{enumerate}

\subsubsection {Scenario 5: A!} 

\begin{enumerate}

\item blabla

\end{enumerate}
